The Form of Uncertainty Affects Selection for Social Learning

### 2023-02-26 ms.tex
Updates from Overleaf

\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \mt{OSF link to PDF when final and separated)}. Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).

>>>>

\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \url{https://osf.io/tpsy9}. Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).
